% ---------------------------------------------------------------------
% Cloned from the HES-SO//Master canvas 2019
% ---------------------------------------------------------------------
\chapter{Introduction}
\label{chap:introduction}

Beginning of 2019, chatbots are everywhere but very limited to narrow tasks, and are, in most cases, sequences of if-else conditions resulting in a very weak \gls{ai}. Indeed, hard-coded connections are requiring an infinite amount of human power to create generic Chatbots able to maintain a conversation at a human level. However, the progress in the field of \gls{ml} is demonstrating that providing large corpora to an unsupervised algorithm is enough to maintain a passive conversation with users, which results into a shifting of the human power into data engineering. Multiple algorithms and technics are emerging monthly, which are demonstrating promising conversational performance improvement; however, they are all still narrow \acrshort{ai}. Indeed, even if they are getting better at providing meaningful sentences, they are still not able to generalize all tasks linked to a conversation, such as, understanding the context, search and learn for missing information, initiate conversation in a meaningful manner, be intuitive, and more. The generalization of those features would allow a significant step forward into general Chatbots.

\section{Aim of Study}
In harmony with the author interest, the goal of this deepening semester project is to suggest and demonstrate strategic approaches as a premise to the \acrshort{agi} and getting a step closer to general Chatbots, which can initiate and maintain human-like conversations in a pro-active manner.

\section{Scope and Study Borders}
As a red line for this deepening project, the focus will be on the Word2Vec technology, from a research perspective. Indeed, this technology is seen as a foundation for the modern \acrshort{nlp} and \acrshort{dnn} Chatbots, which makes it an exciting vector of study about its current usage, its extensions, and potential evolution. 

\section{Industrial Interest}
iCoSys, the Institut of Complex Systems at University of Applied Sciences and Arts at Fribourg, Switzerland, is interested into the result of this project as a study for their AI-News project, whose goal is to provide a chatbot as a tool to reader, to help them narrow their interests and deliver the right information. AI-News is in collaboration with the Swiss Innovation Agency from the Swiss Confederation, and La Liberté, the daily newspaper from Fribourg. 